A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-02-08 jacobian_calc_CMAME.tex
intro to response for I.2

>>>>

The type of material model used in this study is referred to as a linear
peridynamic solid, having what is called a state-based constitutive model. In
order for a definition of this material to be useful here, background material
needs to be laid out to enable the discussion. To begin with, some essential
mathematical definitions will be listed and peridynamic theory summarized. Then
state-based constitutive models will be summarized, followed by a description of
the linear peridynamic solid model used in this work. After the peridynamic
equation of motion and consitutive model in use have been discussed, it is then
possible to give a more precise definition of the tangent stiffness matrix for
the problem being discussed in this work. The following discussion is largely
taken from \cite{silling:psa}, but reproduced here fo clarity.
